Performances Code

### 2019-02-01 Scripts/performances.rmd
added script for results

#comparing top predictors across resolution and cell line
rfeModel_dist_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe10kbvars <- rfeModel_dist_10kb$optVariables[1:32]

rfeModel_dist_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe25kbvars <- rfeModel_dist_25kb$optVariables[1:32]

rfeModel_dist_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe50kbvars <- rfeModel_dist_50kb$optVariables[1:32]

rfeModel_dist_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe100kbvars <- rfeModel_dist_100kb$optVariables[1:32]

rfeModel_dist_10kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe10kbvars_k562 <- rfeModel_dist_10kb_k562$optVariables[1:32]

rfeModel_dist_25kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe25kbvars_k562 <- rfeModel_dist_25kb_k562$optVariables[1:32]

rfeModel_dist_50kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe50kbvars_k562 <- rfeModel_dist_50kb_k562$optVariables[1:32]

rfeModel_dist_100kb_k562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfe100kbvars_k562 <- rfeModel_dist_100kb_k562$variables$var[rfeModel_dist_100kb_k562$variables$Variables==32 & rfeModel_dist_100kb_k562$variables$Resample=="Fold1.Rep1"]

rfe10kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe10kbvars)
rfe25kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe25kbvars)
rfe50kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe50kbvars)
rfe100kbvars <- gsub(paste(c("Gm12878-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe100kbvars)

rfe10kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe10kbvars_k562)
rfe25kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe25kbvars_k562)
rfe50kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe50kbvars_k562)
rfe100kbvars_k562 <- gsub(paste(c("K562-", 
                            "_dist", 
                            "-Sydh", 
                            "-Haib", 
                            "-Broad",
                            "-Uchicago",
                            "-Uta",
                            "-Uw"), collapse = "|"),"", rfe100kbvars_k562)

alltopvars <- data.frame(rfe10kbvars,
                         rfe10kbvars_k562,
                         rfe25kbvars,
                         rfe25kbvars_k562,
                         rfe50kbvars,
                         rfe50kbvars_k562,
                         rfe100kbvars,
                         rfe100kbvars_k562)

rfe10kbvars_o <- sort(rfe10kbvars)
rfe25kbvars_o <- sort(rfe25kbvars)
rfe50kbvars_o <- sort(rfe50kbvars)
rfe100kbvars_o <- sort(rfe100kbvars)
rfe10kbvars_k562_o <- sort(rfe10kbvars_k562)
rfe25kbvars_k562_o <- sort(rfe25kbvars_k562)
rfe50kbvars_k562_o <- sort(rfe50kbvars_k562)
rfe100kbvars_k562_o <- sort(rfe100kbvars_k562)
alltopvars_o <- data.frame(rfe10kbvars_o,rfe25kbvars_o,rfe50kbvars_o,rfe100kbvars_o,
                         rfe10kbvars_k562_o,rfe25kbvars_k562_o,rfe50kbvars_k562_o,rfe100kbvars_k562_o)

grid.newpage()
venn.plot <- draw.quad.venn(
	area1 = length(rfe10kbvars), #The size of the first set
	area2 = length(rfe25kbvars), #The size of the second set
	area3 = length(rfe50kbvars), #The size of the third set
	area4 = length(rfe100kbvars), #The size of the fourth set
	n12 = length(intersect(rfe10kbvars,rfe25kbvars)), #The size of the intersection between the first and the second set
	n13 = length(intersect(rfe10kbvars,rfe50kbvars)), #The size of the intersection between the first and the third set
	n14 = length(intersect(rfe10kbvars,rfe100kbvars)), #The size of the intersection between the first and the fourth set
	n23 = length(intersect(rfe25kbvars,rfe50kbvars)), #The size of the intersection between the second and the third set
	n24 = length(intersect(rfe25kbvars,rfe100kbvars)), #The size of the intersection between the second and the fourth set
	n34 = length(intersect(rfe50kbvars,rfe100kbvars)), #The size of the intersection between the third and the fourth set
	n123 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars))), #The size of the intersection between the first, second and third sets
	n124 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe100kbvars))), #The size of the intersection between the first, second and fourth sets
	n134 = length(Reduce(intersect, list(rfe10kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the first, third and fourth sets
	n234 = length(Reduce(intersect, list(rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between the second, third and fourth sets
	n1234 = length(Reduce(intersect, list(rfe10kbvars,rfe25kbvars,rfe50kbvars,rfe100kbvars))), #The size of the intersection between all four sets
	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
	fill = c("orange", "red", "green", "blue"),
	lty = "dashed",
	cex = 2,
	cat.cex = 2,
	cat.col = c("orange", "red", "green", "blue")
	);

grid.newpage()
venn.plot.k562 <- draw.quad.venn(
	area1 = length(rfe10kbvars_k562), #The size of the first set
	area2 = length(rfe25kbvars_k562), #The size of the second set
	area3 = length(rfe50kbvars_k562), #The size of the third set
	area4 = length(rfe100kbvars_k562), #The size of the fourth set
	n12 = length(intersect(rfe10kbvars_k562,rfe25kbvars_k562)), #The size of the intersection between the first and the second set
	n13 = length(intersect(rfe10kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the first and the third set
	n14 = length(intersect(rfe10kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the first and the fourth set
	n23 = length(intersect(rfe25kbvars_k562,rfe50kbvars_k562)), #The size of the intersection between the second and the third set
	n24 = length(intersect(rfe25kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the second and the fourth set
	n34 = length(intersect(rfe50kbvars_k562,rfe100kbvars_k562)), #The size of the intersection between the third and the fourth set
	n123 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562))), #The size of the intersection between the first, second and third sets
	n124 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, second and fourth sets
	n134 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the first, third and fourth sets
	n234 = length(Reduce(intersect, list(rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between the second, third and fourth sets
	n1234 = length(Reduce(intersect, list(rfe10kbvars_k562,rfe25kbvars_k562,rfe50kbvars_k562,rfe100kbvars_k562))), #The size of the intersection between all four sets
	category = c("10 kb", "25 kb", "50 kb", "100 kb"),
	fill = c("orange", "red", "green", "blue"),
	lty = "dashed",
	cex = 2,
	cat.cex = 2,
	cat.col = c("orange", "red", "green", "blue")
	);

grid.newpage()
venn.plot.10kb <- draw.pairwise.venn(
	area1 = length(rfe10kbvars),
	area2 = length(rfe10kbvars_k562),
	cross.area = length(intersect(rfe10kbvars,rfe10kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.25kb <- draw.pairwise.venn(
	area1 = length(rfe25kbvars),
	area2 = length(rfe25kbvars_k562),
	cross.area = length(intersect(rfe25kbvars,rfe25kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.50kb <- draw.pairwise.venn(
	area1 = length(rfe50kbvars),
	area2 = length(rfe50kbvars_k562),
	cross.area = length(intersect(rfe50kbvars,rfe50kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

grid.newpage()
venn.plot.100kb <- draw.pairwise.venn(
	area1 = length(rfe100kbvars),
	area2 = length(rfe100kbvars_k562),
	cross.area = length(intersect(rfe100kbvars,rfe100kbvars_k562)),
	category = c("GM12878", "K562"),
	fill = c("blue", "red"),
	lty = "blank",
	cex = 2,
	cat.cex = 2,
	cat.just = list(c(-.5, -3), c(2, -3)))

@@

##Heatmaps of top predictors

###10 kb

```{r}
topvars10kbgm12878 <- cbind.data.frame(names(rfeModel_dist_10kb$fit$importance[,1]), rfeModel_dist_10kb$fit$importance)
topvars10kbgm12878 <- topvars10kbgm12878[1:32,]
rownames(topvars10kbgm12878) <- NULL
names(topvars10kbgm12878) <- c("Feature", "Importance")
topvars10kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars10kbgm12878$Feature)

topvars10kbk562 <- cbind.data.frame(names(rfeModel_dist_10kb_k562$fit$importance[,1]), rfeModel_dist_10kb_k562$fit$importance[,4])
topvars10kbk562 <- topvars10kbk562[1:32,]
rownames(topvars10kbk562) <- NULL
names(topvars10kbk562) <- c("Feature", "Importance")
topvars10kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars10kbk562$Feature)

impdata_10kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars10kbgm12878$Feature,
                                                 topvars10kbk562$Feature)))
impdata_10kb$gm12878_10kb <- NA
impdata_10kb$k562_10kb <- NA

impdata_10kb$gm12878_10kb[which(impdata_10kb$Feature %in% topvars10kbgm12878$Feature)] <- topvars10kbgm12878$Importance
impdata_10kb$k562_10kb[which(impdata_10kb$Feature %in% topvars10kbk562$Feature)] <- topvars10kbk562$Importance

impdata_10kb <- impdata_10kb[order(impdata_10kb$Feature),]

#preObj <- preProcess(impdata_10kb, method=c("center", "scale"))
#impdata_10kb <- predict(preObj, impdata_10kb)

impdata_10kb_long <- melt(impdata_10kb)
impdata_10kb_long <- ddply(impdata_10kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars10kbplot <- ggplot(impdata_10kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

###25 kb

```{r}
topvars25kbgm12878 <- cbind.data.frame(names(rfeModel_dist_25kb$fit$importance[,1]), rfeModel_dist_25kb$fit$importance)
topvars25kbgm12878 <- topvars25kbgm12878[1:32,]
rownames(topvars25kbgm12878) <- NULL
names(topvars25kbgm12878) <- c("Feature", "Importance")
topvars25kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars25kbgm12878$Feature)

topvars25kbk562 <- cbind.data.frame(names(rfeModel_dist_25kb_k562$fit$importance[,1]), rfeModel_dist_25kb_k562$fit$importance[,1])
topvars25kbk562 <- topvars25kbk562[1:32,]
rownames(topvars25kbk562) <- NULL
names(topvars25kbk562) <- c("Feature", "Importance")
topvars25kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars25kbk562$Feature)

impdata_25kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars25kbgm12878$Feature,
                                                 topvars25kbk562$Feature)))
impdata_25kb$gm12878_25kb <- NA
impdata_25kb$k562_25kb <- NA

impdata_25kb$gm12878_25kb[which(impdata_25kb$Feature %in% topvars25kbgm12878$Feature)] <- topvars25kbgm12878$Importance
impdata_25kb$k562_25kb[which(impdata_25kb$Feature %in% topvars25kbk562$Feature)] <- topvars25kbk562$Importance

impdata_25kb <- impdata_25kb[order(impdata_25kb$Feature),]

#preObj <- preProcess(impdata_25kb, method=c("center", "scale"))
#impdata_25kb <- predict(preObj, impdata_25kb)

impdata_25kb_long <- melt(impdata_25kb)
impdata_25kb_long <- ddply(impdata_25kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars25kbplot <- ggplot(impdata_25kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

```{r}
topvars50kbgm12878 <- cbind.data.frame(names(rfeModel_dist_50kb$fit$importance[,1]), rfeModel_dist_50kb$fit$importance)
topvars50kbgm12878 <- topvars50kbgm12878[1:32,]
rownames(topvars50kbgm12878) <- NULL
names(topvars50kbgm12878) <- c("Feature", "Importance")
topvars50kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars50kbgm12878$Feature)

topvars50kbk562 <- cbind.data.frame(names(rfeModel_dist_50kb_k562$fit$importance[,1]), rfeModel_dist_50kb_k562$fit$importance[,1])
topvars50kbk562 <- topvars50kbk562[1:32,]
rownames(topvars50kbk562) <- NULL
names(topvars50kbk562) <- c("Feature", "Importance")
topvars50kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars50kbk562$Feature)

impdata_50kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars50kbgm12878$Feature,
                                                 topvars50kbk562$Feature)))
impdata_50kb$gm12878_50kb <- NA
impdata_50kb$k562_50kb <- NA

impdata_50kb$gm12878_50kb[which(impdata_50kb$Feature %in% topvars50kbgm12878$Feature)] <- topvars50kbgm12878$Importance
impdata_50kb$k562_50kb[which(impdata_50kb$Feature %in% topvars50kbk562$Feature)] <- topvars50kbk562$Importance

impdata_50kb <- impdata_50kb[order(impdata_50kb$Feature),]

#preObj <- preProcess(impdata_50kb, method=c("center", "scale"))
#impdata_50kb <- predict(preObj, impdata_50kb)

impdata_50kb_long <- melt(impdata_50kb)
impdata_50kb_long <- ddply(impdata_50kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars50kbplot <- ggplot(impdata_50kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

```{r}
topvars100kbgm12878 <- cbind.data.frame(names(rfeModel_dist_100kb$fit$importance[,1]), rfeModel_dist_100kb$fit$importance)
topvars100kbgm12878 <- topvars100kbgm12878[1:32,]
rownames(topvars100kbgm12878) <- NULL
names(topvars100kbgm12878) <- c("Feature", "Importance")
topvars100kbgm12878$Feature <- gsub(paste(c("Gm12878-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars100kbgm12878$Feature)

topvars100kbk562 <- cbind.data.frame(rfeModel_dist_100kb_k562$variables$var[1:32], rfeModel_dist_100kb_k562$variables$Overall[1:32])
topvars100kbk562 <- topvars100kbk562[1:32,]
rownames(topvars100kbk562) <- NULL
names(topvars100kbk562) <- c("Feature", "Importance")
topvars100kbk562$Feature <- gsub(paste(c("K562-",
                                           "_dist",
                                           "-Haib", 
                                           "-Sydh",
                                           "-Uta",
                                           "-Uw",
                                           "-Broad",
                                           "-Uchicago"), collapse = "|"),
                                   "",
                                   topvars100kbk562$Feature)

impdata_100kb <- data.frame(Feature = Reduce(union, 
                                            list(topvars100kbgm12878$Feature,
                                                 topvars100kbk562$Feature)))
impdata_100kb$gm12878_100kb <- NA
impdata_100kb$k562_100kb <- NA

impdata_100kb$gm12878_100kb[which(impdata_100kb$Feature %in% topvars100kbgm12878$Feature)] <- topvars100kbgm12878$Importance
impdata_100kb$k562_100kb[which(impdata_100kb$Feature %in% topvars100kbk562$Feature)] <- topvars100kbk562$Importance

impdata_100kb <- impdata_100kb[order(impdata_100kb$Feature),]

#preObj <- preProcess(impdata_100kb, method=c("center", "scale"))
#impdata_100kb <- predict(preObj, impdata_100kb)

impdata_100kb_long <- melt(impdata_100kb)
impdata_100kb_long <- ddply(impdata_100kb_long, .(variable), transform,   
                           rescale = rescale(value))

topvars100kbplot <- ggplot(impdata_100kb_long, aes(variable, Feature)) + 
    geom_tile(aes(fill = rescale),
              colour = "white") + scale_fill_gradient2(low = "white", 
                                                      #mid = "white",
                                                      high = muted("red"), 
                                                      #midpoint = 0, 
                                                      space = "Lab",
                                                      na.value = "grey50", 
                                                      guide = "legend", 
                                                      aesthetics = "fill",
                                                      name="Importance",
                                                      labels=c("Very Low",
                                                               "Low",
                                                               "Medium",
                                                               "High",
                                                               "Very High"))+
  scale_x_discrete(name="Cell Line", labels=c("GM12878", "K562"))+
  theme_bw()+
  theme_minimal()
```

```{r}
ggarrange(topvars25kbplot,
          topvars50kbplot,
          topvars100kbplot,
          ncol=3,
          nrow=1,
          common.legend = TRUE,
          legend = "right")
```

@@

>>>>

@@

@@

##10kb

```{r}
#GM12878

##Accuracy
